---
title: "Reconstruct IPD from KM Example"
author: "Xin (David) Zhao"
date: "2026-07-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

The R notebook aims to reconstruct the individual patient data from published Kaplan-Meier curves using the R package `IPDfromKM`. This notebook accompany the blog [article](https://davidzhao1015.github.io/blog/2026/IPD-from-KM-R/).

The analytical workflow follows instructions of `IPDfromKM`, authored by Na Liu et al. The core algorim to reconstruct invidual patient data from the published KM curves was based on Guyot's method, with enhanced modifications. 


## Step-by-step implementation

### Load the library

```{r}

library("IPDfromKM")

```

### Prepare input data

```{r input, echo=FALSE}

radio <- Radiationdata$radio
radioplus <- Radiationdata$radioplus
trisk <- Radiationdata$trisk
nrisk_radio <- Radiationdata$nrisk.radio
nrisk_radioplus <- Radiationdata$nrisk.radioplus

```


### Plot survival curves for two arms 

```{r visual validation}


plot(radio, 
     xlab="Time (month)", ylab="Survival proportion (%)",
     type="l",
     lty=2,
     col="cyan4",
     xlim=c(1, 70),
     ylim=c(0,100),
     main="Curves extracted by ScanIt software")

lines(radioplus, 
      type="l",
      col="red4",
      lty=1)
legend("topright",
       c("Radiotherapy", "Radiotherapy plus cetuximab"),
       col=c("cyan4", "red4"),
       lty = c(2,1),
       text.col =c("cyan4", "red4") ,
       bty = "n")
text(40, 80, "Reported Hazard Ratio with 95% CI:")
text(40, 75, "0.68 (0.52, 0.89)")


```


### Reconstruct IPD from KM curves 

#### Control arm

```{r}

pre_radio <- preprocess(dat = radio, 
                        trisk = trisk,
                        nrisk = nrisk_radio,
                        maxy = 100)
est_radio <- getIPD(prep = pre_radio, armID = 0, tot.events = NULL)

```


#### Treatment arm

```{r}


pre_radio_plus <- preprocess(dat = radioplus, 
                             trisk = trisk,
                             nrisk = nrisk_radioplus,
                             maxy = 100)
est_radio_plus <- getIPD(prep = pre_radio_plus, armID = 1, tot.events = NULL)


```


### Graphic and statistical validation

#### Control arm

```{r}

plot(est_radio)

```


```{r}

summary(est_radio)

```


#### Treatment arm

```{r}

plot(est_radio_plus)


```


```{r}


summary(est_radio_plus)


```

### Output

```{r}

surv2 <-survreport(ipd1 = est_radio$IPD,
                   ipd2 = est_radio_plus$IPD,
                   arms = 2,
                   interval = 8,
                   s = c(0.75, 0.5, 0.25),
                   showplots = TRUE)

```

