---
title: "Reconstructing Individual Patient Data from Published Kaplan–Meier Curves, R Notebook"
author: "Xin (David) Zhao"
date: "2026-08-10"
output: 
    html_document:
        toc: FALSE
        code_folding: "show"
        code_download: TRUE
        theme:
            bg: "#FFFFFF"
            fg: "#24292F"
            base_font:
                google: "Inter"
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.align='center')

```

## 1. Introduction

The programmed analytical workflow closely follows instructions of the R
package `IPDfromKM`, invented by Na Liu et al, which is powered by the
robust Guyot's algorithm.

The R notebook contains explaining documentation along with scrips. For
more detailed interpretations and supportive information, view the blog
[article](https://davidzhao1015.github.io/blog/2026/IPD-from-KM-R/)
accompanying this notebook.

The notebook was built with R `r getRversion()`.


## 2. Step-by-step R implementation

The analytic steps include, 1. Digitize KM curves 2. Validate digitized
data 3. Preprocess coordinates 4. Reconstruct IPD 5. Validate
reconstructed IPD 6. Visualize outcomes

The first step was implemented by the external software, while all other
steps are streamlined in R package `IPDfromKM`.

### 2.1 Load the library

The version of the IPDfromKM used in the notebook, `r packageVersion("IPDfromKM")`.

```{r library}

library("IPDfromKM")

```

### 2.2 Prepare input data

The input data is digitized time-to-event data, and can be accessible
from the package. It is derived from a published clinical study on
effect of a cancer treatment (radiotherapy plus cetuximab) on patients
with skin cancer compared with the cotnrol (radiotherapy alone). The
follow-up dufration is about 60 weeks.

The event of interest is tummor is prevented from returning or
progressing at the original region (logcoregional control).

The input object contains three elements, - time-specific event
proportions for both arms - number of patients at risk for both arms -
time at risk

```{r input}

# Time-specific event proportions for both arms
radio <- Radiationdata$radio
radioplus <- Radiationdata$radioplus

# Number of patients at risk for both arms
trisk <- Radiationdata$trisk
nrisk_radio <- Radiationdata$nrisk.radio

# Time at risk 
nrisk_radioplus <- Radiationdata$nrisk.radioplus

```

### 2.3 Validate digitized data

```{r visual validation}

plot(radio, 
     xlab="Time (month)", ylab="Survival proportion (%)",
     type="l",
     lty=2,
     col="cyan4",
     xlim=c(1, 70),
     ylim=c(0,100),
     main="Curves extracted by ScanIt software")

lines(radioplus, 
      type="l",
      col="red4",
      lty=1)
legend("topright",
       c("Radiotherapy", "Radiotherapy plus cetuximab"),
       col=c("cyan4", "red4"),
       lty = c(2,1),
       text.col =c("cyan4", "red4") ,
       bty = "n")
text(40, 80, "Reported Hazard Ratio with 95% CI:")
text(40, 75, "0.68 (0.52, 0.89)")


```

### 2.4 Preprocess coordinates & Reconstruct IPD {.tabset}

Convert the extracted input data into the format required for IPD
reconstruction using the preprocess() function, which aligns the
digitized coordinates with reported numbers at risk so that Guyot’s
algorithm can correctly estimate censoring patterns.

Apply Guyot’s algorithm to reconstruct IPD, the core step in the
procedure to estimate events and censoring based on predefined
assumptions.

#### Control arm

```{r prep for control}

pre_radio <- preprocess(dat = radio, 
                        trisk = trisk,
                        nrisk = nrisk_radio,
                        maxy = 100)
est_radio <- getIPD(prep = pre_radio, armID = 0, tot.events = NULL)

```

#### Treatment arm

```{r prep for treatment}


pre_radio_plus <- preprocess(dat = radioplus, 
                             trisk = trisk,
                             nrisk = nrisk_radioplus,
                             maxy = 100)
est_radio_plus <- getIPD(prep = pre_radio_plus, armID = 1, tot.events = NULL)


```

### 2.5 Validate reconstructed IPD {.tabset}

The summary presents a quantitative comparison between the reconstructed
and digitized KM curves, based on root-mean-square error (RMSE), mean
absolute error (MAE), and maximum absolute error. Together, these
metrics indicate excellent agreement between the reconstructed and
original survival curves.

The IPDfromKM package provides graphical diagnostics to assess how well
the reconstructed IPD reproduces the published KM curves and the
digitized source data.

#### Control arm

```{r}

plot(est_radio)

```

```{r}

summary(est_radio)

```

#### Treatment arm

```{r}

plot(est_radio_plus)


```

```{r}


summary(est_radio_plus)


```

### 2.6 Visualize outcomes

Once the reconstructed IPD has been validated, it can be used to answer
several clinically and statistically important questions that are often
not directly reported in the original publication.

```{r}

surv2 <-survreport(ipd1 = est_radio$IPD,
                   ipd2 = est_radio_plus$IPD,
                   arms = 2,
                   interval = 8,
                   s = c(0.75, 0.5, 0.25),
                   showplots = TRUE)

```


### Author Bio

[Xin (David) Zhao, PhD](https://davidzhao1015.github.io/), integrates epidemiology, evidence synthesis, quantitative modeling, and health economics to develop transparent, reproducible analytics that support healthcare and biotech decision-making.



